Study locations

### 2024-04-16 Manuscript/Ms.qmd
edits

#Add descriptor
my_tibble = d %>%
  mutate(Description = case_when(
    Variable == "Study_id" ~ "Identifier of the study",
    Variable == "Network_id" ~ "Identifier of a site sampled within a study",
    Variable == "Sampling_method" ~ "Type of plant-pollinator sampling",
    Variable == "Authors_habitat" ~ "Type of habitat as described by the authors",
    Variable == "SafeNet_habitat" ~ "Type of habitat homogenized across studies",
    Variable == "Bioregion" ~ "European biogiographical regions",
    Variable == "Country" ~ "Country where the plant-pollinator interaction was observed",
    Variable == "Locality" ~ "Locality where the plant-pollinator interaction was observed",
    Variable == "Latitude-Longitude" ~ "Coordinates of the observed interaction in decimal degrees",
    Variable == "Date" ~ "Year, month and day when the observation took place",
    Variable == "Interaction" ~ "Number of interactions. By default is 1 as interactions are provided ungrouped",
    Variable == "Plant_old_name" ~ "Plant species name given by the authors",
    Variable == "Plant_accepted_name" ~ "Harmonized plant species name in the database",
    Variable == "Plant_rank" ~ "Taxonomic rank of the observation",
    Variable == "Plant_order" ~ "Order taxonomic rank of the observed plant species",
    Variable == "Plant_family" ~ "Family taxonomic rank of the observed plant species",
    Variable == "Plant_genus" ~ "Genus taxonomic rank of the observed plant species",
    Variable == "Plant_unsure_id" ~ "Category to indicate if the plant species name is unsure (Yes) or not (No)",
    Variable == "Plant_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
    Variable == "Pollinator_old_name" ~ "Pollinator species name given by the authors",
    Variable == "Pollinator_accepted_name" ~ "Harmonized pollinator species name in the database",
    Variable == "Pollinator_rank" ~ "Taxonomic rank of the observation",
    Variable == "Pollinator_order" ~ "Order taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_family" ~ "Family taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_genus" ~ "Genus taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_unsure_id" ~ "Category to indicate if the pollinator species name is unsure (Yes) or not (No)",
    Variable == "Pollinator_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
        Variable == "Flower_data" ~ "Floral data availability (Yes) or (No)",
        Variable == "Flower_data_merger" ~ "Column to merge floral data with the interaction dataset",

@@

#Coverage across bee genera
d1 = readRDS("../Data/Manuscript_info/bee_data.RData")
all_rows_bees = d1 %>%  
filter(fam_group == "a") %>% 
nrow(.)
#
data_bees = d1 %>%  
filter(fam_group == "a") %>% 
mutate(Percent = case_when(is.na(Percent) ~ 0, TRUE ~ Percent)) %>% 
filter(Percent > 0) %>% 
nrow(.)
#
bee_genera_percent_coverage = data_bees/all_rows_bees
#Check average coverage across bee genera
average_coverage_bee_genera = d1 %>% 
filter(fam_group == "a") %>% 
mutate(Percent = case_when(is.na(Percent) ~ 0, TRUE ~ Percent)) %>% 
ungroup() %>% 
summarise(average_coverage_bee_genera = mean(Percent)) %>% 
pull()

@@

The database contains a total of `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species. The database coverage of all flowering plant species occurring in Europe is `r format(round(plant_coverage, 2), nsmall=2)`% (**Figure 4**), with an average coverage of `r format(round(mean_plant_fam_cov, 2), nsmall=2)`% at the plant family level. Approximately, half of the plant families have at least one species with interaction records (`r format(round(percent_plant_fam_with_data, 2), nsmall=2)`%), and the presence or absence of interaction data for the different plant species seems not to follow a statistically relevant phylogenetic pattern ($\lambda$ = `r format(round(lambda_phylosig_plants, 2), nsmall=2)`; _P_ = `r format(round(p_phylosig_plants, 2), nsmall=2)`). The coverage of the main taxonomic groups of pollinators at European level is `r format(round(bee_coverage, 2), nsmall=2)`% for bees, `r format(round(syrphid_coverage, 2), nsmall=2)`% for syrphids and `r format(round(lepidoptera_coverage, 2), nsmall=2)`% for butterflies (see **Figure S1** for coverage at the family level for bees and butterflies, and at the subfamily level for syrphids). Bees constitute `r format(round(bee_interactions_percent, 2), nsmall=2)`% of the interactions of the database, and `r format(round(bee_interactions_non_apis_percent, 2), nsmall=2)`% of the interactions when excluding honey bees.

`r format(round(bee_genera_percent_coverage, 2), nsmall=2)`% of bee genera have at least one species with interaction records within the database and the average coverage at the genus level is `r format(round(average_coverage_bee_genera, 2), nsmall=2)`%. Notably, the presence or absence of interactions records seems or not seems to follow any sort of phylogenetic signal (($\lambda$ = `r format(round(lambda_phylosig_bees, 2), nsmall=2)`; _P_ = `r format(round(p_phylosig_bees, 2), nsmall=2)`)).

**Figure 3**

@@

#Check number of studies by habitat
habitat = data %>% 
select(Study_id, SafeNet_habitat) %>% 
distinct() %>%  
group_by(SafeNet_habitat) %>% 
summarise(Habitat_count = n()) 
#Check number of studies by bioregion
bioregion = data %>% 
select(Study_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) 
#Check pols by habitat
pollinator_percent = data %>%
group_by(SafeNet_habitat, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(SafeNet_habitat) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Check pols by bioregion
pollinator_percent_bio = data %>%
group_by(Bioregion, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(Bioregion) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Preparing datasets for horizontal plot
a1 = habitat %>% 
mutate(Group = "Habitat") %>% 
rename(Habitat = SafeNet_habitat) %>% 
rename(Count = Habitat_count)

@@

b2 = pollinator_percent %>% 
mutate(Group = "Habitat") %>% 
rename(Habitat = SafeNet_habitat)
#Bind rows
c2 = bind_rows(a2, b2)

>>>>

#Add descriptor
my_tibble = d %>%
  mutate(Description = case_when(
    Variable == "Study_id" ~ "Identifier of the study",
    Variable == "Network_id" ~ "Identifier of a site sampled within a study",
    Variable == "Sampling_method" ~ "Type of plant-pollinator sampling",
    Variable == "Authors_habitat" ~ "Type of habitat as described by the authors",
    Variable == "EuPPollNet_habitat" ~ "Type of habitat homogenized across studies",
    Variable == "Bioregion" ~ "European biogiographical regions",
    Variable == "Country" ~ "Country where the plant-pollinator interaction was observed",
    Variable == "Locality" ~ "Locality where the plant-pollinator interaction was observed",
    Variable == "Latitude-Longitude" ~ "Coordinates of the observed interaction in decimal degrees",
    Variable == "Date" ~ "Year, month and day when the observation took place",
    Variable == "Interaction" ~ "Number of interactions. By default is 1 as interactions are provided ungrouped",
    Variable == "Plant_old_name" ~ "Plant species name given by the authors",
    Variable == "Plant_accepted_name" ~ "Harmonized plant species name in the database",
    Variable == "Plant_rank" ~ "Taxonomic rank of the observation",
    Variable == "Plant_order" ~ "Order taxonomic rank of the observed plant species",
    Variable == "Plant_family" ~ "Family taxonomic rank of the observed plant species",
    Variable == "Plant_genus" ~ "Genus taxonomic rank of the observed plant species",
    Variable == "Plant_unsure_id" ~ "Category to indicate if the plant species name is unsure (Yes) or not (No)",
    Variable == "Plant_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
    Variable == "Pollinator_old_name" ~ "Pollinator species name given by the authors",
    Variable == "Pollinator_accepted_name" ~ "Harmonized pollinator species name in the database",
    Variable == "Pollinator_rank" ~ "Taxonomic rank of the observation",
    Variable == "Pollinator_order" ~ "Order taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_family" ~ "Family taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_genus" ~ "Genus taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_unsure_id" ~ "Category to indicate if the pollinator species name is unsure (Yes) or not (No)",
    Variable == "Pollinator_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
        Variable == "Flower_data" ~ "Floral data availability (Yes) or (No)",
        Variable == "Flower_data_merger" ~ "Column to merge floral data with the interaction dataset",

@@

#Coverage across bee genera
d1 = readRDS("../Data/Manuscript_info/bee_data.RData")
all_rows_bees = d1 %>%  
filter(fam_group == "a") %>% 
nrow(.)
#
data_bees = d1 %>%  
filter(fam_group == "a") %>% 
mutate(Percent = case_when(is.na(Percent) ~ 0, TRUE ~ Percent)) %>% 
filter(Percent > 0) %>% 
nrow(.)
#
bee_genera_percent_coverage = data_bees/all_rows_bees * 100
#Check average coverage across bee genera
average_coverage_bee_genera = d1 %>% 
filter(fam_group == "a") %>% 
mutate(Percent = case_when(is.na(Percent) ~ 0, TRUE ~ Percent)) %>% 
ungroup() %>% 
summarise(average_coverage_bee_genera = mean(Percent)) %>% 
pull()

@@

The database contains a total of `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator and `r prettyNum(plant_spp_number, big.mark=",")` plant species. The coverage of the main pollinators groups occurring in Europe is `r format(round(bee_coverage, 2), nsmall=2)`% for bees, `r format(round(syrphid_coverage, 2), nsmall=2)`% for syrphids and `r format(round(lepidoptera_coverage, 2), nsmall=2)`% for butterflies (see **Figure S1** for coverage at the family level for bees and butterflies, and at the subfamily level for syrphids). Bees constitute `r format(round(bee_interactions_percent, 2), nsmall=2)`% of the interactions of the database, and `r format(round(bee_interactions_non_apis_percent, 2), nsmall=2)`% of the interactions when excluding honey bees. Within the database, `r format(round(bee_genera_percent_coverage, 2), nsmall=2)`% of bee genera have at least one species with interaction records, and the average coverage at the bee genus level is `r format(round(average_coverage_bee_genera, 2), nsmall=2)`% (**Figure 3**). In addition, the presence or absence of interactions records for bees seems not to follow any sort of phylogenetic pattern ($\lambda$ = `r format(round(lambda_phylosig_bees, 2), nsmall=2)`; _P_ = `r format(round(p_phylosig_bees, 2), nsmall=2)`). The database coverage of all flowering plant species occurring in Europe is `r format(round(plant_coverage, 2), nsmall=2)`% (**Figure 4**), with an average coverage of `r format(round(mean_plant_fam_cov, 2), nsmall=2)`% at the plant family level. Approximately, half of the plant families have at least one species with interaction records (`r format(round(percent_plant_fam_with_data, 2), nsmall=2)`%), and the presence or absence of interaction data for the different plant species also seems not to follow a statistically relevant phylogenetic pattern ($\lambda$ = `r format(round(lambda_phylosig_plants, 2), nsmall=2)`; _P_ = `r format(round(p_phylosig_plants, 2), nsmall=2)`).

@@

#Check number of studies by habitat
habitat = data %>% 
select(Study_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) 
#Check number of studies by bioregion
bioregion = data %>% 
select(Study_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) 
#Check pols by habitat
pollinator_percent = data %>%
group_by(EuPPollNet_habitat, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(EuPPollNet_habitat) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Check pols by bioregion
pollinator_percent_bio = data %>%
group_by(Bioregion, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(Bioregion) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Preparing datasets for horizontal plot
a1 = habitat %>% 
mutate(Group = "Habitat") %>% 
rename(Habitat = EuPPollNet_habitat) %>% 
rename(Count = Habitat_count)

@@

b2 = pollinator_percent %>% 
mutate(Group = "Habitat") %>% 
rename(Habitat = EuPPollNet_habitat)
#Bind rows
c2 = bind_rows(a2, b2)

### 2024-04-16 Scripts/Figures/Map_study_locations.Rmd
edits

colors <- c(
"#8AD69E", "#74C5CE",  "#FDE9DE",
"#45A631", "#95F7F0", "#CB53E1",
"#FE90BB", "#B187E1", "#F8A982", 
"#0075DC", "#993F00",  "#5EF1F2", 
"#005C31", "#74C5CE", "black", 
"lightblue",  "darkorange3","#8F7C00",
"#8F7C00","#8F7C00", "#9DCC00", 
"#C20088", "gold1","#FFA8BB",
"#426600","#94FFB5","#003380",  
"salmon", "palegreen","greenyellow",
"mediumaquamarine", "tomato", "orange", 
"blue", "black", "green",
"purple", "red", "gray","violetred",
"coral4", "plum1", "yellow",
"brown3", "orange3", "red4", "darkviolet")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)

>>>>

colors <- c(
"#8AD69E", "#74C5CE",  "#FDE9DE",
"#45A631", "#95F7F0", "#CB53E1",
"#FE90BB", "#B187E1", "#F8A982", 
"#0075DC", "#993F00",  "#5EF1F2", 
"#005C31", "#74C5CE", "black", 
"lightblue",  "darkorange3","#8F7C00",
"#8F7C00","#8F7C00", "#9DCC00", 
"#C20088", "gold1","#FFA8BB",
"#426600","#94FFB5","#003380",  
"salmon", "palegreen","greenyellow",
"mediumaquamarine", "tomato", "orange", 
"blue", "black", "green",
"purple", "red", "gray","violetred",
"coral4", "plum1", "yellow",
"brown3", "orange3", "red4", "darkviolet",
"darkgreen")
#To generate more random colors 
#randomcoloR::distinctColorPalette(k = length(file_names), altCol = F, runTsne = T)
